Practical Machine Learning Project
--------------------------------------------------------



Summary
--------------------------------------------------------
Six young health participants were asked to perform one set of 10 repetitions of the Unilateral Dumbbell Biceps Curl in five different fashions: 

* exactly according to the specification (Class A)
* throwing the elbows to the front (Class B)
* lifting the dumbbell only halfway (Class C)
* lowering the dumbbell only halfway (Class D)
* throwing the hips to the front (Class E)

Due to extremely long running time with caret's train function, parallel processing and randomForest's randomForest method are chosen(~1 min).
Libraries, Options and Data Load

This script assumes that the training set and the test set are in the same directory. 

```{r}
library(ggplot2)
library(caret)
library(randomForest)
library(Hmisc)
library(foreach)
library(doParallel)
```

```{r}
#options(warn=1)
#options(stringsAsFactors = FALSE)
testing <-read.csv("C:/Users/HP/Desktop/Coursera/Practical Machine Learning/pml-testing.csv")
training <- read.csv("C:/Users/HP/Desktop/Coursera/Practical Machine Learning/pml-training.csv")
```



Cleaning Data and Select Features
--------------------------------------------------------
A brief look at the data revealed many columns with mainly NA's and finally lead to select only the main acceleration columns.

```{r}
set.seed(357)
training <- training[,union(grep("^accel_", colnames(training)),grep("classe",colnames(training)) )] 
testing <- testing[,union(grep("^accel_", colnames(testing)),grep("classe",colnames(testing)) )] 
names(training)
```


Data Partition
--------------------------------------------------------
```{r}
##Split trainingset into training sample(80%) and test sample(20%)
partition <- createDataPartition(y = training$classe, p = 0.75, list = FALSE)
sample1 <- training[partition, ]
psample1 <-  training[-partition, ]
```

* Converting features
```{r}
##Classification-feature (classe) to factor, all others as numeric
sample1$classe <-as.factor(sample1$classe)
sample1[, 1:6] <- sapply(sample1[, 1:6], as.numeric)
psample1$classe <-as.factor(psample1$classe)
psample1[, 1:6] <- sapply(psample1[, 1:6], as.numeric)
```


Model Build
--------------------------------------------------------



```{r}
##Significant speedup using Parallel Processing
registerDoParallel()
rf <- foreach(ntree=rep(150, 6), .combine=randomForest::combine, .packages='randomForest') %dopar% {
        randomForest(x=sample1[,1:12], y=sample1$classe, ntree=ntree)
}
```



Model Evaluate
--------------------------------------------------------
```{r}
pred0 <- predict(rf,psample1)
confusionMatrix(pred0,psample1$classe)
```



Predict Answers to submit
--------------------------------------------------------
```{r}
predict(rf, testing)
```





Conclusion
--------------------------------------------------------
Because of an accuracy of around 96% it was expected nearly all of the answers to be correct. However there was an error found for answer 3.